Correlates of replicability: evidence from student replication projects

### 2023-03-23 paper/manuscript.Rmd
work on intro

---
title: PUT YOUR TITLE HERE
author:
  - name: Veronica Boyce
    affiliation: Stanford
    footnote:
      - corresp
  - name: Maya Mathur
    affiliation: Stanford
  - name: Michael C. Frank
    affiliation: Stanford
address:
  - code: Stanford
    address: Stanford University
footnote:
  - code: corresp
    text: "Corresponding author. Email: vboyce@stanford.edu"
bibliography: ["251MA.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
csl: dmk-format.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
link-citations: TRUE
output:
  bookdown::pdf_document2:
    toc: FALSE
    keep_tex: TRUE
    template: generic_article_template.tex
    #md_extensions: "-autolink_bare_uris"
    number_sections: TRUE
    citation_package: default # Can also be "natbib"
lang: en # Main document language in BCP47 format
geometry: "margin=25mm"
papersize: a4
#linestretch: 2 # for double spacing
endfloat: FALSE # Set to TRUE to turn on latex endfloat package to place figures and tables at end of document
# endfloatoption: # See endfloat documentation for more possibilities
#   - tablesfirst # Default
#   - nomarkers # Default
numberlines: FALSE
authblk: TRUE # FALSE = author affiliations in footnotes; TRUE = author affiliations in a block below author names
footnotehyper: FALSE # TRUE will give you enhanced table footnote capabilities. Set to FALSE to be able to use French blocks. Needed due to what appears to be a latex bug.
urlcolor: blue
linkcolor: blue
citecolor: blue
graphics: TRUE # Needed to be able to include images
tables: TRUE # Needed to be able to include tables
# fancyhdr:
#   first:
#     #headleft: "REPORT-NO-XXXX"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 0pt
#     #footleft: A left foot
#     footrulewidth: 0pt
#   subsequent:
#     #headleft: "NEXT-PAGE-HEADER-LEFT"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 1pt
#     footrulewidth: 0pt

@@

::: {.abstract data-latex="" lang=en}
TODO abstract
:::

<!-- Use class keywords to format keywords section -->
::: {.keywords data-latex="" lang=en}
One keyword; Yet another keyword
:::

@@

# TODO list
- title
- abstract
- need to do supplement with the stuff we preregistered (sensitivity analysis, all models)
- how to introduce coding methods (outcome measures)
- many citations everywhere
- long list of things to gesture at in intro
- link to open stuffs
- ** verify code for ES ** with someone
- note that 4ish of these papers were previously reported in RP:P

@@

predict w/ ML @altmejd2019
prediction with humans @dreber2015; @forsell2019

@@

[structure w/i intro?]

[replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution] Psychology is in the middle of some heated debate around the fields practices and many reform efforts. Many of these issues concern the truthworthiness or not of the published literature, with transparency, openness efforts. A lot of this centers around issues of reproducibility and replicability.  Concerns around the practices of science. Replication is a hot topic. Some argue that it is a cornerstone of a cumulative science, and findings of low replication rates are a problem. Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.

[ there's ... not a lot of empirics] One of the concerns is that published literature may not replicate as much as previously thought or as desired. To quantify and understand this problem, we need empirical data about replication attempts. However, due to the arduous nature of collecting samples of replications, there have not been many large-scale replication efforts, so all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.

[do we discuss reasons for replications and why many, while valuable in specific phenomena, help less with this question?]
Many replications of individual effects have been performed, but these are less useful as pattern analysis because the varied sampling and reporting, and the fact they aren't all in one place. Also pub bias.

@@

@@

We used a subjective rating of replication success as our primary outcome measure. The instruction team had coded a holistic measure of replication success for each project when they were turned in at the end of the course. For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (ToDO foobar % of cases). This measure was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.

As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (NUMBER, see Figure \ref{fig:prisma}). We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic [@errington2021].

@@

library(kableExtra)
knitr::kable(cors, digits = 3, align='rcc',format="latex", position="!h", caption="The correlation of individual predictors with subjective replication outcomes. For subfield, cognitive psychology is treated as the baseline condition.") |> kable_styling(full_width=F, font_size=10)

@@

Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample FOOBAR %).

@@

### Measures of replication success
Our primary replication outcome is experimenter and instructor rated replication success (0-1). The subjective replication success was recorded by the teaching staff for the majority of class replications at the time they were conducted. Where the values were missing they were filled in by MCF on the basis of the reports. For all studies, replication success was independently coded by VB on the basis of the reports. Where VB’s coding disagreed with the staff/MCF’s code, the difference was resolved by discussion between VB and MCF. These were coded on a [0, .25, .5, .75, 1] scale. TODO rate of coding discrepancy

>>>>

---
title: "Correlates of replicability: evidence from student replication projects"
author:
  - name: Veronica Boyce
    affiliation: Stanford
    footnote:
      - corresp
  - name: Maya Mathur
    affiliation: Stanford
  - name: Michael C. Frank
    affiliation: Stanford
address:
  - code: Stanford
    address: Stanford University
footnote:
  - code: corresp
    text: "Corresponding author. Email: vboyce@stanford.edu"
bibliography: ["251MA.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
csl: dmk-format.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
link-citations: TRUE
output:
  bookdown::pdf_document2:
    toc: FALSE
    keep_tex: TRUE
    template: generic_article_template.tex
    #md_extensions: "-autolink_bare_uris"
    number_sections: TRUE
    citation_package: default # Can also be "natbib"
lang: en # Main document language in BCP47 format
geometry: "margin=25mm"
papersize: a4
#linestretch: 2 # for double spacing
endfloat: FALSE # Set to TRUE to turn on latex endfloat package to place figures and tables at end of document
# endfloatoption: # See endfloat documentation for more possibilities
#   - tablesfirst # Default
#   - nomarkers # Default
numberlines: FALSE
authblk: TRUE # FALSE = author affiliations in footnotes; TRUE = author affiliations in a block below author names
footnotehyper: FALSE # TRUE will give you enhanced table footnote capabilities. Set to FALSE to be able to use French blocks. Needed due to what appears to be a latex bug.
urlcolor: blue
linkcolor: blue
citecolor: blue
graphics: TRUE # Needed to be able to include images
tables: TRUE # Needed to be able to include tables
# fancyhdr:
#   first:
#     #headleft: "REPORT-NO-XXXX"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 0pt
#     #footleft: A left foot
#     footrulewidth: 0pt
#   subsequent:
#     #headleft: "NEXT-PAGE-HEADER-LEFT"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 1pt
#     footrulewidth: 0pt

@@

::: {.abstract data-latex="" lang=en}

A cumulative science relies on knowing how much to trust published findings. Large-scale replication studies provide a measure of how reliable the published literature in a field is by determining what fraction of studies replicate. Because of the effort involved in conducting a large number of replications, few large-scale replications are available. We add 176 replication projects conducted by students of experimental studies primarily in psychology. Roughly half the studies were replicated successfully, and we report how features of the studies and the replications influenced the replication outcome.

:::

<!-- Use class keywords to format keywords section -->
<!--::: {.keywords data-latex="" lang=en}
One keyword; Yet another keyword
:::-->

@@

# TODO list
- BETTER title
- BETTER abstract
- need to do supplement with the stuff we preregistered (sensitivity analysis, all models) -- waiting on finalized stats predictors
- many citations everywhere
- long list of things to gesture at in intro
- link to open stuffs
- ** verify code for ES ** with someone

@@

predict w/ ML @altmejd2019

@@

Psychology is in the middle of heated debate over its research practices and the subject of many reform efforts.  Many of these issues concern how trustworth the published literature is (or isn't), how it got to be this way, and what measures can be taken to improve the quality of findings for the future. These issues center around issues of reproducibility  and replicability. Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.

 A major concern is that published literature may not replicate as much as previously thought or as desired. This has been illustrated by prominent findings/theories not replicating at all (ego depletion/ TMT?). To understand how replicable the literature as a whole is, we need empirical data about replication attempts across a wide range of studies. Most replications are targeted replications of individual results of interest to the researcher, but these are not sampled randomly from the literature, are performed in inconsistent ways, and may be selectively published depending on the results. Thus, they are not ideal for estimating the overall replicability of the field.

There have been a limited number of large-scale replication efforts, which sample studies from a discipline to estimate overall replicability. Due to the arduous process of replicating many studies, there have not been many large-scale replication efforts. Thus, all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.

@@

```{r}
matching <- d |> filter(status!="unusable") |> mutate(match=ifelse(replicated_instructor_code==replicated_report_code,1,0)) |> group_by(match) |> tally()

pred_int_avail <- d |> filter(!is.na(predInt)&!is.na(p_orig)) |> tally()

@@

We used a subjective rating of replication success as our primary outcome measure. The instruction team had coded a holistic measure of replication success for each project when they were turned in at the end of the course. For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (`r pluck(matching,2,1)/176*100 |> round()` % of cases). This measure was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.

As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (`r pluck(pred_int_avail,1)` cases, see Figure \ref{fig:prisma}). We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic [@errington2021].

@@

library(kableExtra)
knitr::kable(cors, digits = 3, align='rcc',format="latex", position="!h", caption="The correlation of individual predictors with subjective replication outcomes. For subfield, cognitive psychology is treated as the baseline condition. See Methods for how these variables were coded.") |> kable_styling(full_width=F, font_size=10)

@@

Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample TODO FOOBAR %).

We note that 4 (TODO check) of the replication projects were included in RP:P, and FOOBAR of them were previously reported in @hawkins.

@@

### Measures of replication success
Our primary replication outcome is experimenter and instructor rated replication success (0-1). The subjective replication success was recorded by the teaching staff for the majority of class replications at the time they were conducted. Where the values were missing they were filled in by MCF on the basis of the reports. For all studies, replication success was independently coded by VB on the basis of the reports. Where VB’s coding disagreed with the staff/MCF’s code, the difference was resolved by discussion between VB and MCF (`r pluck(matching,2,1)/176*100 |> round()`% of studies). These were coded on a [0, .25, .5, .75, 1] scale.

### 2023-03-23 paper/manuscript.tex
work on intro

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  english,
  a4paper,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={PUT YOUR TITLE HERE},
  pdflang={en},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={blue},
  urlcolor={blue},
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=25mm]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\usepackage{footnote} % For some unknown reason, footnotehyper clashes with French
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% dont indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\title{PUT YOUR TITLE HERE}

@@

\begin{abstract}
TODO abstract

@@

\begin{keywords}
One keyword; Yet another keyword

\end{keywords}

@@

\begin{itemize}
\tightlist
\item
  title
\item
  abstract
\item
  need to do supplement with the stuff we preregistered (sensitivity analysis, all models)
\item
  how to introduce coding methods (outcome measures)
\item
  many citations everywhere
\item
  long list of things to gesture at in intro
\item
  link to open stuffs
\item
  ** verify code for ES ** with someone
\item
  note that 4ish of these papers were previously reported in RP:P
\end{itemize}

@@

predict w/ ML Altmejd et al. (\protect\hyperlink{ref-altmejd2019}{2019})
prediction with humans Dreber et al. (\protect\hyperlink{ref-dreber2015}{2015}); Forsell et al. (\protect\hyperlink{ref-forsell2019}{2019})

@@

{[}structure w/i intro?{]}

{[}replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution{]} Psychology is in the middle of some heated debate around the fields practices and many reform efforts. Many of these issues concern the truthworthiness or not of the published literature, with transparency, openness efforts. A lot of this centers around issues of reproducibility and replicability. Concerns around the practices of science. Replication is a hot topic. Some argue that it is a cornerstone of a cumulative science, and findings of low replication rates are a problem. Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.

{[} there's \ldots{} not a lot of empirics{]} One of the concerns is that published literature may not replicate as much as previously thought or as desired. To quantify and understand this problem, we need empirical data about replication attempts. However, due to the arduous nature of collecting samples of replications, there have not been many large-scale replication efforts, so all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.

{[}do we discuss reasons for replications and why many, while valuable in specific phenomena, help less with this question?{]}
Many replications of individual effects have been performed, but these are less useful as pattern analysis because the varied sampling and reporting, and the fact they aren't all in one place. Also pub bias.

@@

We used a subjective rating of replication success as our primary outcome measure. The instruction team had coded a holistic measure of replication success for each project when they were turned in at the end of the course. For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (ToDO foobar \% of cases). This measure was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.

As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (NUMBER, see Figure \ref{fig:prisma}). We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-errington2021}{Errington et al. 2021}).

@@

\caption{\label{tab:cor}The correlation of individual predictors with subjective replication outcomes. For subfield, cognitive psychology is treated as the baseline condition.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{r|c|c}
\hline
Predictors & r & p\\
\hline
Within subjects & 0.333 & 0.000\\
\hline
Log trials & 0.182 & 0.015\\
\hline
Open data & 0.150 & 0.047\\
\hline
Non psych & 0.080 & 0.294\\
\hline
Other psych & 0.075 & 0.322\\
\hline
Publication year & 0.064 & 0.399\\
\hline
Open materials & 0.002 & 0.979\\
\hline
Stanford & -0.027 & 0.725\\
\hline
Log rep/orig sample & -0.047 & 0.536\\
\hline
Log original sample size & -0.108 & 0.155\\
\hline
Switch to online & -0.158 & 0.037\\
\hline
Social & -0.246 & 0.001\\
\hline
Single vignette & -0.267 & 0.000\\
\hline
\end{tabular}
\end{table}

@@

Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample FOOBAR \%).

@@

Our primary replication outcome is experimenter and instructor rated replication success (0-1). The subjective replication success was recorded by the teaching staff for the majority of class replications at the time they were conducted. Where the values were missing they were filled in by MCF on the basis of the reports. For all studies, replication success was independently coded by VB on the basis of the reports. Where VB's coding disagreed with the staff/MCF's code, the difference was resolved by discussion between VB and MCF. These were coded on a {[}0, .25, .5, .75, 1{]} scale. TODO rate of coding discrepancy

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  english,
  a4paper,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Correlates of replicability: evidence from student replication projects},
  pdflang={en},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={blue},
  urlcolor={blue},
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=25mm]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\usepackage{footnote} % For some unknown reason, footnotehyper clashes with French
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% dont indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\title{Correlates of replicability: evidence from student replication projects}

@@

\begin{abstract}
A cumulative science relies on knowing how much to trust published findings. Large-scale replication studies provide a measure of how reliable the published literature in a field is by determining what fraction of studies replicate. Because of the effort involved in conducting a large number of replications, few large-scale replications are available. We add 176 replication projects conducted by students of experimental studies primarily in psychology. Roughly half the studies were replicated successfully, and we report how features of the studies and the replications influenced the replication outcome.

@@

@@

\begin{itemize}
\tightlist
\item
  BETTER title
\item
  BETTER abstract
\item
  need to do supplement with the stuff we preregistered (sensitivity analysis, all models) -- waiting on finalized stats predictors
\item
  many citations everywhere
\item
  long list of things to gesture at in intro
\item
  link to open stuffs
\item
  ** verify code for ES ** with someone
\end{itemize}

@@

predict w/ ML Altmejd et al. (\protect\hyperlink{ref-altmejd2019}{2019})

@@

Psychology is in the middle of heated debate over its research practices and the subject of many reform efforts. Many of these issues concern how trustworth the published literature is (or isn't), how it got to be this way, and what measures can be taken to improve the quality of findings for the future. These issues center around issues of reproducibility and replicability. Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.

A major concern is that published literature may not replicate as much as previously thought or as desired. This has been illustrated by prominent findings/theories not replicating at all (ego depletion/ TMT?). To understand how replicable the literature as a whole is, we need empirical data about replication attempts across a wide range of studies. Most replications are targeted replications of individual results of interest to the researcher, but these are not sampled randomly from the literature, are performed in inconsistent ways, and may be selectively published depending on the results. Thus, they are not ideal for estimating the overall replicability of the field.

There have been a limited number of large-scale replication efforts, which sample studies from a discipline to estimate overall replicability. Due to the arduous process of replicating many studies, there have not been many large-scale replication efforts. Thus, all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.

@@

We used a subjective rating of replication success as our primary outcome measure. The instruction team had coded a holistic measure of replication success for each project when they were turned in at the end of the course. For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (25.5681818 \% of cases). This measure was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.

As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (134 cases, see Figure \ref{fig:prisma}). We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-errington2021}{Errington et al. 2021}).

@@

\caption{\label{tab:cor}The correlation of individual predictors with subjective replication outcomes. For subfield, cognitive psychology is treated as the baseline condition. See Methods for how these variables were coded.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{r|c|c}
\hline
Predictors & r & p\\
\hline
Within subjects & 0.333 & 0.000\\
\hline
Log trials & 0.182 & 0.015\\
\hline
Open data & 0.150 & 0.047\\
\hline
Non psych & 0.080 & 0.294\\
\hline
Other psych & 0.075 & 0.322\\
\hline
Publication year & 0.064 & 0.399\\
\hline
Open materials & 0.002 & 0.979\\
\hline
Stanford & -0.027 & 0.725\\
\hline
Log rep/orig sample & -0.047 & 0.536\\
\hline
Log original sample size & -0.108 & 0.155\\
\hline
Switch to online & -0.158 & 0.037\\
\hline
Social & -0.246 & 0.001\\
\hline
Single vignette & -0.267 & 0.000\\
\hline
\end{tabular}
\end{table}

@@

Students were free to choose what study they replicated; the recommended path for students who did not have their own ideas was to pick an interesting study from a recent year of Psychological Science (this led to a high fraction of Psych Science articles in the replication sample TODO FOOBAR \%).

We note that 4 (TODO check) of the replication projects were included in RP:P, and FOOBAR of them were previously reported in Hawkins et al. (\protect\hyperlink{ref-hawkins}{n.d.}).

@@

Our primary replication outcome is experimenter and instructor rated replication success (0-1). The subjective replication success was recorded by the teaching staff for the majority of class replications at the time they were conducted. Where the values were missing they were filled in by MCF on the basis of the reports. For all studies, replication success was independently coded by VB on the basis of the reports. Where VB's coding disagreed with the staff/MCF's code, the difference was resolved by discussion between VB and MCF (25.5681818\% of studies). These were coded on a {[}0, .25, .5, .75, 1{]} scale.
